%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%             Ángel Castañeda Résumé
%        src available at git.acsq.me/cv
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{angelpack}

%%%%%%%%%%%%   Paragraph Gap Spacing   %%%%%%%%%%%
\newcommand{\itemspace}{\vspace{0.1870em}}

%%%%%%%%%%%%   Small Caps Redefine     %%%%%%%%%%%
\renewcommand{\textsc}[1]{\uppercase{\footnotesize#1}\normalsize}
% some fonts are complete trash and scrap this, so I need to use this

%%%%%%%%%%%  Triple Items for Exams %%%%%%%%%%%%%%
\newcommand\textbox[1]
    {\parbox{.375\textwidth}{#1}} % < value has to be set manually depending on font

%% Shows borders - useful for troubleshooting %%%%
%\usepackage{showframe}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                      Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

\vspace{-2.8mm}
\noindent\hrulefill

\vspace{-4.5mm}
\noindent\hrulefill

\itemspace
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%               Summary/Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objective}

\hangindent=\parindent % adds indent to second line
%Senior math student seeking full time position for the summer of
%2024. Considerable experience in programming \& maintaining projects,
%strong leadership skills, and a passion to learn. Fluent in Spanish.
To secure a full-time programming position for the summer of 2024.
Considerable experience in programming \& maintaining projects,
strong leadership skills, and a passion to learn. Fluent in Spanish.

\itemspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                 Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}

\subsection{Languages:} \:
\textsc{sql} · \textsc{r} · Python · \textsc{html} · \textsc{css} ·
JavaScript · \textsc{go} · \LaTeX{} · Bash · Scheme Lisp

\subsection{Programs:} \:
Excel · Access · RStudio · git ·  Linux · \textsc{MATLAB} · Neovim

\itemspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                Actuarial Exams
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Actuarial Exams}

%%%%%%%%%%%%     Three Exams    %%%%%%%%%%%%%%%%%%

\textbox{\subsection{P:} {Mar 2022}\hfill}
\textbox{\hfil \subsection{FM:} {Feb 2023}}
\textbox{\hfill\subsection{FAM:} {Mar 2024 (sitting)}}

\itemspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                   Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

%%%%%%%%%%%%%%%%%       MSOE       %%%%%%%%%%%%%%%
\subsection{Milwaukee School of Engineering} \hfill Milwaukee, WI

B.S. Actuarial Science · GPA: 3.4 \hfill \textit{Expected May 2024}

\begin{itemize}[noitemsep,nolistsep]
  \item VP of education, exams, and studying for Mathematics \& Actuarial
    Science Club senior year.

  \item German Club VP senior year, Historical Society photographer junior
    year, and Student Union

    Board treasurer sophomore year.

  \item Independent study on measure theory with mathematics professor.
\end{itemize}

\textbf{\textit{Select Coursework}:} \,Database Mgmt. (\textsc{ms sql}) ·
Time Series Analysis (\textsc{R}) · Professional Presentations

\itemspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%               Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work \& Internship Experience}

%%%%%%%%%%     Tax Preparer w/ Centro    %%%%%%%%%
\subsection{Tax Preparer \& Sys Admin}
· Centro San Miguel, Milwaukee, WI \hfill \textit{Nov 2019 -- Present}

\begin{itemize}[noitemsep,nolistsep]
  \item Prepare individual taxes, notarize affidavits, and translate documents
    from Spanish to English

  \item Set up and maintain website and email services on VPS.
\end{itemize}

\itemspace

%%%%%%%%%%%%      Tutor w/ RCAS   %%%%%%%%%%%%%%%%
\subsection{University Tutor}
· MSOE, Milwaukee, WI \hfill \textit{Nov 2022 -- May 2023}

\begin{itemize}[noitemsep,nolistsep]
  \item CRLA certified tutor for FM study sessions and college math classes.
\end{itemize}

\itemspace

%%%%%%%%%%%%   Internship w/ GLAS   %%%%%%%%%%%%%%
\subsection{Office Management Intern}
· GLAS Education, Williams Bay, WI  \hfill \textit{Jun 2019 -- Aug 2019}

\begin{itemize}[noitemsep,nolistsep]
  \item Handled daily office duties including mail, business/school outreach,
    and supply organization.

  \item Organized team of high school students to educate public about light
    pollution.
\end{itemize}

\itemspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                  Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Featured Projects}

%%%%%%%%%%%%%%       SICP          %%%%%%%%%%%%%%%%
\subsection{\textit{Structure \& Interpretation of Computer Programs}} ·
\href{https://git.acsq.me/sicp/about/}{git.acsq.me/sicp}
\hfill \textit{Aug 2023 -- Present}

\begin{itemize}[noitemsep,nolistsep]
  \item Self-studying MIT's classic book to get a better fundamental
    understanding of recursion, black-box abstraction, and the gaps between computer
    science and mathematics with scheme lisp.
\end{itemize}

\itemspace

%%%%%%%%%%%%%%         Site Hosting    %%%%%%%%%%%%
\subsection{Web \& Email Server Hosting} ·
\href{https://www.acsq.me/sites}{www.acsq.me/sites}
\hfill \textit{Apr 2023 -- Present}

\begin{itemize}[noitemsep,nolistsep]
  \item Create and maintain dynamic blogs/websites and email servers for
    friends and family.

  \item Use Nginx, \textsc{go} http servers, and SQLite3/BoltDB for databases.

  \item Made custom golang package and git submodule for a blog database with SQLite3.
\end{itemize}

\itemspace

%%%%%%%%%   Measure Theory w/ Dr. Armstrong %%%%%%
%\subsection{Measure Theory Independent Study}  \hfill \textit{Mar 2022 -- May 2022}
%\begin{itemize}[noitemsep,nolistsep]
%  \item Worked with math professor to learn triangle inequality proofs,
%  epsilon-delta ball proofs, and an introduction to Lebesgue measures.
%\end{itemize}
%\itemspace

%%%%%%%%%%%  P&C Climate Change Prez   %%%%%%%%%%%
\subsection{\textit{The Claim Before the Storm} Webinar} \hfill \textit{Oct 2021}

\begin{itemize}[noitemsep,nolistsep]
  \item Virtual presentation on climate change and how P\&C companies are
    adapting to it.

  %\item Audience intended to be seniors in high school interested in
  %  actuarial science.

  \item Custom-designed slides, group activities, and broken down info for
    audience comprehension.
\end{itemize}

\itemspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%               Hobbies/Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hobbies \& Interests}

Reading · History · Deutsch · Photography · The Beatles · Cultural Exchange

\end{document}
